Apparent preferences for cognitive effort fade when multiple forms of effort

### 2021-03-18 Cost_manuscript.Rmd
latex quirk

where the section in parentheses was the proportion of the experiment completed so far (note that the organization of the experimental session was fully disclosed), with high values of the free parameter $\alpha_w$ denoting a late integration of the global converging bias. Since participants in the between-subjects experiment experienced a single type of demand, the values of $c_\text{demand}$ and $c_\text{global}$ where the same and $\alpha_w$ did not play a role. This resulted in just fitting parameters $c_\text{demand}$ and $\beta$ for that dataset. For the within-subjects group, we assumed that the resulting $c_\text{demand}$ values from the first experiment reflected the actual bias induced by each demand. We therefore fixed each value of $c_\text{demand}$ (i.e. $c_{cognitive}$, $c_{wait}$, and $c_{physical}$) to the mean of the fitted parameters from each demand group from Experiment 1, and fit the global bias $c_\text{global}$, the convergence rate $\alpha_w$, and temperature $\beta$. This dynamic allowed for the observed merging of acceptances across demands in Experiment 2, while respecting the stability in the between-subjects study.

>>>>

where the section in parentheses was the proportion of the experiment completed so far (note that the organization of the experimental session was fully disclosed), with high values of the free parameter $\alpha_w$ denoting a late integration of the global converging bias. Since participants in the between-subjects experiment experienced a single type of demand, the values of $c_\text{demand}$ and $c_\text{global}$ where the same and $\alpha_w$ did not play a role. This resulted in just fitting parameters $c_\text{demand}$ and $\beta$ for that dataset. For the within-subjects group, we assumed that the resulting $c_\text{demand}$ values from the first experiment reflected the actual bias induced by each demand. We therefore fixed each value of $c_\text{demand}$ (i.e. $c_\text{cognitive}$, $c_\text{wait}$, and $c_\text{physical}$) to the mean of the fitted parameters from each demand group from Experiment 1, and fit the global bias $c_\text{global}$, the convergence rate $\alpha_w$, and temperature $\beta$. This dynamic allowed for the observed merging of acceptances across demands in Experiment 2, while respecting the stability in the between-subjects study.
